Unicode Implementation Issues \thanks { This is a working document for the Rexx Language Association (RexxLA). There will be one or more separate requirements documents. It is written in \LaTeX\ \fmtversion\ and was rendered \today\ using \enginedetails. }

### 2024-04-12 ARB/standards/work-in-progress/document/tex/standard/directives.tex
updates

Return \texttt{\textquotesingle{}1\textquotesingle{}} if the
\emph{production} identitied by \emph{Identifier} contained a
\emph{bnf\_primary} identified by \texttt{BNF\_primary}, otherwise
return \texttt{\textquotesingle{}0\textquotesingle{}}.

@@

\lstinputlisting[language=rexx,label=configotherblankcharacters.rexx,caption=configotherblankcharacters.rexx]{configotherblankcharacters.rexx}
our model are only distinquished by the values within their pool so we
can construct the builtin classes incomplete and then complete them with
directives.}

\emph{Can we initialize the methods of .nil by directives?}

>>>>

Return \texttt{\textquotesingle{}1\textquotesingle{}} if the
\emph{production} identified by \emph{Identifier} contained a
\emph{bnf\_primary} identified by \texttt{BNF\_primary}, otherwise
return \texttt{\textquotesingle{}0\textquotesingle{}}.

@@

\lstinputlisting[language=rexx,label=configotherblankcharacters.rexx,caption=configotherblankcharacters.rexx]{configotherblankcharacters.rexx}
model are only distinquished by the values within their pool so we can
construct the builtin classes incomplete and then complete them with
directives.\_

\_Can we initialize the methods of .nil by directives?\_
